Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-12 README.Rmd
updated descriptions of code files

- `data-preparation.R` contains R code for preparing the raw bullet data (bullet training data, bullet testing data, and example matching signatures) to be used in the paper
- `figure-compression.R` contains R code for compressing the static figure used in the paper
- `submission-steps.R` contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal.

>>>>

- `data-preparation.Rmd` contains R code for preparing the raw bullet data (bullet training data, bullet testing data, and example matching signatures) to be used in the paper and saves zip versions of the data sets to be uploaded to GitHub
- `figure-compression.Rmd` contains R code for compressing the static figure used in the paper to be uploaded to GitHub
- `submission-steps.Rmd` contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal.
